Distinction Centrality Analysis

### 2025-07-17 analysis.qmd
new stuff who dis

---
title: "Jilbert's Distinction Centrality"
execute: 
  eval: true
  echo: true
  output: true
  warning: false
  message: false
format: 
   html:
      code-line-numbers: true
bibliography: networks.bib
---

@@

According to @jilbert24, the Distinction Centrality ($D_i$) of a node is given by the difference between the *status* ($S_i(G)$) and the *constraint* ($C_i(G)$) experienced by each node:

$$
   D_i = S_i(G)  - C_i(G)
$$

Status is measured using the usual Bonacich eigenvector centrality (normalized to have maximum 1.0) computed in the full graph $G$. Constraint, in turn, is given by the average status of $i$'s neighbor in the *node deleted subgraph* that excludes $i$.

$$
C_i(G) = \frac{\sum_{j \in N(i)} S_j(G - i)}{N} 
$$

Where $N(i)$ is the set of $i$'s neighbors, and $S_j(G -i)$ is the eigenvector centrality of node $j$ in the node deleted subgraph of $G$ that excludes $i$. Nodes are more constrained to the extent that others gain status in their absence. The Distinction of a node thus increases with its own status and decreases to the extent that others would gain status if that node was not around.

The normalized version of Distinction Centrality ($D^*$) multiplies each node's status score by the parameter $\theta$, which is ratio of the average of constrain scores and the average of status scores of each node in the the network:

$$
\gamma = \frac{\frac{1}{N}\sum_i C_i(G)}{\frac{1}{N}\sum_i S_i(G)}
$$

The normalized distinction is then given by:

$$
D^*_i = \gamma S_i(G)  - C_i(G)
$$

@@

```{r}
   source("distinction.new.R")
   distinction.new(g2, norm = TRUE)
   distinction.new(g2, norm = FALSE)
```

@@

```{r}
   source("distinction.R")
   g <- as.matrix(read.csv(here("Data", "searchmodeltest.csv")))
   g <- graph_from_edgelist(g, directed = FALSE)
   distinction(g)
```

>>>>

---
title: "Distinction Centrality Analysis"
execute: 
  eval: true
  echo: false
  output: true
  warning: false
  message: false
---

@@

@@

@@

```{r}
   g <- as.matrix(read.csv(here("Data", "searchmodeltest.csv")))
   g <- graph_from_edgelist(g, directed = FALSE)
   distinction(g)
```
